%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{hyperref} 

\name{Pavel Yakovlev} % Your name
\address{yvpavel@gmail.com} % Your phone number and email
\address{\href{https://www.paulyakovlev.com}{paulyakovlev.com} \\ \href{https://www.github.com/paulyakovlev}{github.com/paulyakovlev}} % Your phone number and email


\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

    {\bf University of California, Santa Cruz} \hfill {\em Graduated June 2020} \\ 
    Bachelor's in Computer Science

\end{rSection}



%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}
    \begin{rSubsection}{Lawrence Livermore National Lab - Computing Intern}{June 2019 - September 2019}{Java, JUnit, SQL}{Livermore, CA}
        \item Worked on improving automated testing and software integration framework for large scientific facility.
        \item Contributed to JUnit test suite and provided technical documentation.
        \item Development focused on industry-standard continuous integration and test-driven development practices.
    \end{rSubsection}

    \begin{rSubsection}{remote.it - Sofware Engineering Intern}{May 2018 - June 2019}{ReactJS, Python, AWS, Docker, Terraform}{Palo Alto, CA}
        \item Built an administrative web dashboard to monitor user device activity.
        \item Wrote a library of user-end Python and Shell scripts.
        \item Worked remotely from September 2018 through the end of the internship.
    \end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}
    \begin{rSubsection}{Santa Cruz Stranding Map}{\href{https://github.com/lmlstrandingnetwork/lml-stranding-map}{github.com/lmlstrandingnetwork/lml-stranding-map}}{ReactJS, ExpressJS, Firebase}{}
        \item Geospatial data analysis tool for the UCSC Long Marine Lab.
    \end{rSubsection}

    \begin{rSubsection}{Pollen Planter (Cruzhacks 2020 Winner)}{\href{https://www.devpost.com/software/pollenplanter}{devpost.com/software/pollenplanter}}{React Native, Firebase}{}
        \item Mobile app that recommends pollinator(bees,butterflies)-friendly plants for your garden.
    \end{rSubsection}

    \begin{rSubsection}{Netguard (Treehacks 2019)}{\href{https://www.devpost.com/software/netguard}{devpost.com/software/netguard}}{Python, Flask, Twilio, Docker}{}
        \item Cyber attack protection for internet-connected devices at home.
    \end{rSubsection}

    \begin{rSubsection}{Distributed Key-Store}{\href{https://github.com/paulyakovlev/distributed-rpi-kvstore}{github.com/paulyakovlev/distributed-rpi-kvstore}}{Python, Flask, Docker}{}
        \item Sharded, fault-tolerant key-value store that runs on a cluster of Raspbery Pi devices.
    \end{rSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}
    \begin{description}
    \item[Languages:] C++, Java, Python, Javascript, HTML, CSS
    \item[Frameworks and Tools:] ReactJS, NodeJS, Flask, SQL, git, Docker, REST, Agile
    \end{description}
\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
