%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{hyperref} 

\name{Pavel Yakovlev} % Your name
\address{(707)~$\cdot$~971~$\cdot$~9336 \\ yvpavel@gmail.com} % Your phone number and email
\address{\href{https://www.paulyakovlev.com}{paulyakovlev.com} \\ \href{https://www.github.com/paulyakovlev}{github.com/paulyakovlev}} % Your phone number and email


\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of California, Santa Cruz} \hfill {\em Fall 2018 - Present} \\ 
Bachelor's in Computer Science

{\bf Santa Rosa Junior College} \hfill {\em Fall 2015 - Spring 2018}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Lawrence Livermore National Lab}{June 2019 - September 2019}{Computing Intern}{Livermore, CA}
    \item Worked on the enhancement and modernization of automated testing and software integration frameworks.
    \item Unified the build processes around industry-standard continuous integration and test-driven practices using Jenkins, JUnit.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{remote.it}{May 2018 - June 2019}{Sofware Engineering Intern}{Palo Alto, CA}
    \item In a team of three, developed a web app prototype to monitor client/user activity.
    \item Created a CI/CD pipeline to build and test a Docker image with CircleCI + Goss.
    \item Worked with Terraform + Packer for AWS EC2 AMI deployment and testing.
    \item Created a library of user-end Python and Shell scripts for bulk device management.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}

\begin{rSubsection}{NetGuard (Treehacks '19)}{\href{https://www.devpost.com/software/netguard}{devpost.com/software/netguard}}{}{}
    \item Alerts owner of IoT device of cyber attack and locks down the device.
    \item Written in Python, runs on Raspberry Pi, SMS alerts achieved with Twilio API.
    \item Worked with another team member to write the listener and API request component.
\end{rSubsection}

\begin{rSubsection}{Save Our Species}{\href{https://github.com/hamfox/save-our-species}{github.com/hamfox/save-our-species}}{}{}
    \item Mobile app for the purpose of reporting marine mammal strandings with accurate data
    \item Worked within a team of 6, strictly following Agile practices to deliver a working product 
    \item Was responsible for backend infastructure of data model and contributed to UI components of the app
    \item Initial version of the app built with Swift, then rebuilt with React Native.
\end{rSubsection}

\end{rSection}


%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Technical Strengths}

%\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
%Computer Languages & C/C++, Python, Java \\
%Protocols \& APIs & XML, JSON, SOAP, REST \\
%Databases & MySQL, PostgreSQL, Microsoft SQL \\
%Tools & , Vim, Emacs
%\end{tabular}

%\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
