%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{hyperref} 

\name{Pavel Yakovlev} % Your name
\address{yvpavel@gmail.com} % Your phone number and email 


\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Professional Background}
    Recent graduate with versatile and creative background eager to find new 
    opportunities for growth. 
    Knowledgeable in many aspects of business operations with a strong background in customer service.
    Committed to maintaining a high level of 
    customer satisfaction, and creating a welcoming environment for everyone.

\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
    {\bf Santa Rosa Junior College} \hfill {\em September 2015 - May 2018} \\ 
    Computer Science Transfer Program

    {\bf University of California, Santa Cruz} \hfill {\em September 2018 - June 2020} \\ 
    Bachelor's in Computer Science

\end{rSection}



%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}
    \begin{rSubsection}{Lawrence Livermore National Lab}{June 2019 - September 2019}{Computing Intern}{Livermore, CA}
        \item Worked on improving automated testing and software integration framework for large scientific facility.
        \item Frequently communicated with different dev teams to understand how to best develop their testing framework.
        \item Delivered meaningful results in a highly technical and fast paced environment.
    \end{rSubsection}

    \begin{rSubsection}{remote.it}{May 2018 - June 2019}{Sofware Engineering Intern}{Palo Alto, CA}
        \item Developed user facing software tools.
        \item Wrote extensive technical documentation for users.
        \item Collaborated with PR interns on delivering user-focused marketing/product campaign. 
    \end{rSubsection}

    \begin{rSubsection}{Petaluma Coffee and Tea Company}{June 12 2018 - August 2018}{Barista/Sales}{Petaluma, CA}
        \item Fulfilled wholesale coffee bean orders via phone and website.
        \item Operated and maintained commercial coffee brewers and espresso machine.
        \item Prepared specialty espresso drinks and pour-over coffee.
        \item Maintained registers and performed the end of the day deposit.
        \item Provided detailed information about coffee beans, beverages, and brew systems to customers.

    \end{rSubsection}

    \begin{rSubsection}{Santa Rosa Junior Col}{January 2018 - May 2018}{Math Tutor/Teaching Assistant}{Santa Rosa, CA}
        \item Provided instructional assistance for a college algebra class. 
        \item Assisted students with assignments, answering course questions in an empathetic and professional way.
        \item Developed and led weekly study sessions on campus.
        
    \end{rSubsection}

\end{rSection}


%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}
    \begin{description}
    \item Over 4 years working in a customer service environment.
    \item Productive relationship and partner-building skills; excel at understanding customer needs.
    \item Creative problem solving, and conflict resolution
    \end{description}
\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
